---
title: "Working Title"
author: "Levi C. Nicklas"
date: "12/19/2020"
output: pdf_document
---

\newpage

```{r, include=F, message = F, warning = F}
# Libraries
library(tidyverse)
library(here)
library(igraph)
library(tictoc)

# ggplot theme


```


# Table of Contents

1. Abstract

2. Introduction

3. Literature Review

4. Data

  a. reddit
  
  b. NHTSA Reports

5. Data Preprocessing

6. Methods

  a. Graph Kernels
  
    - Random Walk kernel
    
    - Graphlet kernel
    
    - LW kernel
    
  b. Clustering
  
    - Kernel Density Estimation (Clustering in R^1)
    
    - Clustering in R^2

7. Analysis
  
  a. Graph Kernel Performance (LDA comparison?)
  
  b. Clustering Performance

8. Conclusion

\newpage

# Abstract

 

# Introduction

# Literature Review

# Data

## reddit

**(1/16/21)** Data was obtained from `reddit.com` using the `{RedditExtractoR}` package, querying for posts featuring one of eightteen words in the subreddit `r/mentalhealth`. Posts were additionally restricted to having at least 10 comments. Datasets were composed and saved to `.RDS` objects for later use. The focus of the study will be the similarity of a post as measured by the comments which belong to the post.


## NHTSA

```{r nhtsa-import}

```


# Data Preprocessing

**(1/16/21)** Both datasets are converted to graph representations of the text. The graph representation is a skip-bigram graph composed of the observational unit of text. 

## reddit 
```{r reddit-reformat}
reddit_graphs <- readRDS(here::here("Data/ProcessedData/reddit_graphs.RDS"))

reddit_graphs[[2]][[1]] %>% plot()
```

## NHSTA
```{r nhtsa-reformat}


```

# Methods

## Graph Kernels

### reddit
```{r, message = F, warning = F, message = F}
# TEST RUN
# reddit_graphs_s <- list(reddit_graphs[[1]][[1]],
#                         reddit_graphs[[2]][[1]],
#                         reddit_graphs[[3]][[1]],
#                         reddit_graphs[[4]][[1]],
#                         reddit_graphs[[5]][[1]],
#                         reddit_graphs[[6]][[1]],
#                         reddit_graphs[[7]][[1]])
# 
# my_pars <- list(reddit_graphs_s,reddit_graphs_s[[1]])
# 
# my_pars[[1]][[1]] %>% is.igraph()
# my_pars[[2]] %>% is.igraph()
# 
# graphkernels::CalculateEdgeHistKernel(list(my_pars[[1]][[3]],my_pars[[2]]))
# 
# compute_graph_similarity(my_pars)

# Do 3 at once, TEST
set.seed(23)
reddit_graphs_s <- sample(reddit_graphs, 500)

tic()
compute_kernel()
toc()
beepr::beep(sound=3)
result <- readRDS(here::here("Data/ProcessedData/reddit_graphkernel.RDS"))

result[[1]] %>% 
  as.data.frame() %>% 
  ggplot() + 
  geom_density(aes(x = `.`), binwidth = 30)

# Results from Tic-Toc assessment.
compute_time <- data.frame(n = c(10, 50, 75, 100, 200, 300, 500),
                           t = c(0.405, 9.336, 19.833, 26.69,140.33, 263.008, 819.526))

compute_time %>% 
  ggplot(aes(t, n))+
  geom_point() +
  #geom_line() +
  geom_smooth(method = NULL, formula = y ~ log(x))
```

```{r}


```



## Clustering

# Analysis

# Conclusion

-------------------------------------------



# WIP

```{r}
mental_health_df <- mental_health[[1]]

for(i in 2:length(mental_health)){
  #print(nrow(mental_health_df))
  mental_health_df <- rbind(mental_health_df, mental_health[[i]])
}

rm(mental_health, i)
```

```{r}
# mental_health_df
source(here::here("Development/Scripts/df_to_graph_list.R"))

result <- df_to_graph_list(mental_health_df$comment[1:10],2,2)

# Plot example
plot.igraph(result[[8]])
```

