---
title: "Dev Notebook - 1"
output: html_notebook
---

```{r Setup, message = F}
library(igraph)
library(tidyverse)
library(ggraph)
library(graphkernels)

data(mutag)
```


# Intro

In this notebook I am exploring developing the graph kernel and random walk processes in R, without relying on another's package. I am doing this because it will give me better command of the material and the `{graph kernels}` package is written in C++ ... which I really can't read at that level.

So for the graph kernel I will need to have a graph and then perform a random walk on the graph before I can compute a kernel. So this is the first target.

# Random Walk

For this project I will be using the `{igraph}` package to let me focus more on the operations on the graphs instead of creating the graphs myself.

I will use the `mutag` dataset for this development. This dataset features _rich_ graphs with node and edge attributes. In the future, the node attribute for my thesis will be a word; this will be fine for now. Below is a plot of one of the `mutag` graphs. 
```{r Plot Ex 1}
plot(mutag[[2]])
```

To complete a random walk, I will need to pick a node at random, and then randomly pick one of it's neighbors to visit, and repeat until the length I specify is met. So first let's pick a node at random!

```{r Get init node}
set.seed(23)

# Get graph from mutag
sample_graph <- mutag[[2]]

# Find out how many nodes there are. May be a better function for this.
num_nodes <- dim(igraph::as_adjacency_matrix(sample_graph))

# Pick a random node.
random_node <- sample(seq(from = 1,
                   to = num_nodes[1]),1)

# Perform random walk.
my_rw <- igraph::random_walk(graph = sample_graph, 
                    start = random_node, 
                    steps = 1000)
```

Now that we performed a random walk with the help of `{igraph}`, I want to visualize it.


```{r visualize RW}
# count how many times a node was visited.
node_counts <- as_tibble(unlist(as.list(my_rw))) %>% 
  count(value)

vertex.attributes(sample_graph)$count <- node_counts$n

sample_graph %>% 
  ggraph()+
  geom_node_point(aes(color = count), size = 3.5) +
  geom_edge_link(color = "grey") +
  geom_node_text(aes(label = label), color = "black", size = 5, nudge_x = 0.2) +
  scale_color_gradient(low = "#ffccff",
                       high = "#4d004d") +
  theme_void() +
  labs(title = "Levi's First Random Walk: N=1000")
  


```

# Other section (???)

In the slides from _Vishwanathan_, available  [here](https://github.com/Levi-Nicklas/GraphKernels/blob/master/RelevantPapers_and_Resources/vish_presentation.pdf), he outlines the steps to compute a random walk graph kernel using prinicples from linear algebra. Let's dive in. I'll build a small section on each important mathematical concept in the slides.

## Probability of Next Step

_Vishwanathan_ shows in the slides that we can use the adjacency matrix, $A$, to find the probability of going from one node to another in $n$ step length random walk. For examle, in the example above (`mutag[2]`), we can find the probability of going from node 10 to node 13 like so:

```{r mutag2_adj_mat}
#Get the adjacency matrix.
mutag2_adj_mat <- igraph::as_adjacency_matrix(sample_graph) %>% 
  as.matrix()

#Build matrix exponentiation.
exp_mat <- function(your_matrix, n){
  tmp <- your_matrix
  
  for(i in 1:(n-1)){
   tmp <- tmp %*% your_matrix
  }
  
  return(tmp)
}

#Check... 
#exp_mat(mutag2_adj_mat,4) == (mutag2_adj_mat %*% mutag2_adj_mat %*% mutag2_adj_mat %*% mutag2_adj_mat)

#Calculate random walks of length 7.
exp_mat(mutag2_adj_mat, 7)
```

Now that we computed $A^n$, we need to compute $\tilde{A}^n$, which is the probability of walks length $n$. This is done by $\tilde{A} = A D^{-1}$, where $D$ is the diagonal matrix of node degrees.

```{r norm_adj_mat}
mutag2_deg_mat<- igraph::degree(sample_graph) %>% 
  diag()

# Check that solve() does what I think it does lol.
# mutag2_deg_mat %*% solve(mutag2_deg_mat)
# returns identity matrix... all good here :)

# Normalize Adj matrix by degree matrix.
mutag2_adjnorm_mat <- mutag2_adj_mat %*% solve(mutag2_deg_mat)
```

Great! Now when we compute $\tilde{A}^{n}$ we are computing the probability of a walk from $i$ to $j$ (the entry in the matrix, that is).

```{r prob_i_to_j_test}
# Check that probability sums to 1.
# exp_mat(mutag2_adjnorm_mat, 7) %>%
#  as.data.frame() %>% 
#  summarise_all(.funs = sum)

# Check probabilty of taking a walk of length 7
# from node 10 to node 15.
exp_mat(mutag2_adjnorm_mat, 7)[15,17]

# Check probabilty of taking a walk of length 7
# from node 10 to node 20.
exp_mat(mutag2_adjnorm_mat, 7)[15,20]
```

```{r make_some_visual}
#exp_mat(mutag2_adjnorm_mat, 7) %>% 
#  image()

# make a test df to try visualizations.
test_df <- exp_mat(mutag2_adjnorm_mat, 7) %>% 
  as.data.frame() 

# store the row names.
test_df$row <- rownames(test_df)

# change colnames to integers
colnames(test_df) <- c(1:26, "row")

# pivot_longer()
test_df_long<- test_df %>% 
  pivot_longer(cols = (1:26)) %>% 
  mutate(row = as.numeric(row),
         column = as.numeric(name)) %>% 
  select(row, column, value)

test_df_long %>% 
  ggplot(aes(x = column, y = row, fill = value)) +
  geom_tile(color = "white") +
  scale_fill_viridis() +
  theme_minimal()+
  labs(x = "column", y = "row",
       title = "Probability of Walk (n=7) from i to j")

# ^^ Clean this up with more frequent labels on axis
# remove excess gridlines
# change scale from [0,1]
```




```{r}
# Not like this...Im pretty sure.
t(spectrum(sample_graph)$vectors / (factorial(7))) %*%  exp_mat(mutag2_adjnorm_mat, 7) %>% 
  sum()
```

```{r}
data(mutag)
K <- CalculateVertexHistKernel(mutag[1:7])

K
```
