---
title: "Working Title"
author: "Levi C. Nicklas"
date: "12/19/2020"
output: pdf_document
---

\newpage

```{r, include=F, message = F, warning = F}
# Libraries
library(tidyverse)
library(here)
library(furrr)

# ggplot theme


```


# Table of Contents

1. Abstract

2. Introduction

3. Literature Review

4. Data

  a. reddit
  
  b. NHTSA Reports

5. Data Preprocessing

6. Methods

  a. Graph Kernels
  
    - Random Walk kernel
    
    - Graphlet kernel
    
    - LW kernel
    
  b. Clustering
  
    - Kernel Density Estimation (Clustering in R^1)
    
    - Clustering in R^2

7. Analysis
  
  a. Graph Kernel Performance (LDA comparison?)
  
  b. Clustering Performance

8. Conclusion

\newpage

# Abstract

# Introduction

# Literature Review

# Data

## reddit

```{r reddit-import}
# Data Read In
mental_health <- readRDS(here::here("Data/RawData/mentalhealth_reddit_20201025.RDS"))
```
## NHTSA

```{r nhtsa-import}

```


# Data Preprocessing

## reddit 
```{r reddit-reformat, message = F, warning = F, error= F}
# Get first table.
mental_health_df <- mental_health[[1]]

# Append other tables.
for(i in 2:length(mental_health)){
  #print(nrow(mental_health_df))
  mental_health_df <- rbind(mental_health_df, mental_health[[i]])
}

# Trash old objects.
rm(i, mental_health)

# furrr
source(here::here("Development/Scripts/df_to_graph_list.R"))

plan(multicore)

mental_health_graphs <- future_map(.x = mental_health_df$comment,
                                   .f = df_to_graph_list)


```

## NHSTA
```{r nhtsa-reformat}


```

# Methods

## Graph Kernels

## Clustering

# Analysis

# Conclusion

-------------------------------------------



# WIP

```{r}
mental_health_df <- mental_health[[1]]

for(i in 2:length(mental_health)){
  #print(nrow(mental_health_df))
  mental_health_df <- rbind(mental_health_df, mental_health[[i]])
}

rm(mental_health, i)
```

```{r}
# mental_health_df
source(here::here("Development/Scripts/df_to_graph_list.R"))

result <- df_to_graph_list(mental_health_df$comment[1:10],2,2)

# Plot example
plot.igraph(result[[8]])
```

