---
title: "NHTSA Reports"
output: html_notebook
---


#### Purpose: This notebook will use scripts from the `Development/Scripts` folder and read data from the `Data/NHTSA` folders to analyze the NHTSA reports. The NHTSA reports are strating as just text from the "summary" portion of the reports.

# Initial Processing

```{r, warning = F, message = F}
# Libraries
library(tidyverse)
library(here)
library(igraph)
library(graphkernels)

# Data Import
file.names <- list.files(path = here::here("Data/NHTSA/RawData"))
papers <- list()

for(i in 1:length(file.names)){
  temp.file.name <- here::here(paste0("Data/NHTSA/RawData/", file.names[i]))

  if(grepl("paper_",temp.file.name)){
    temp.file <- readRDS(temp.file.name)
    
    temp.file <- paste(temp.file, collapse = ". ")
    
    papers[i] <- temp.file
  }
}
```

We read the papers into memory. Now lets put them together in a nice way... perhaps a dataframe.

```{r}
papers <- data.frame(id = 1:length(papers),
           text = unlist(papers))

#saveRDS(papers, file = here::here("Data/NHTSA/RawData/ConsolidatedPapers.rds")) # object too big for github.
```

Now we can clean the data. Tokenizing, removing stop words, stemming words, etc.

```{r, message = F, warning = F}
#papers <- readRDS(here::here("Data/NHTSA/RawData/ConsolidatedPapers.rds")) # onject too big for github.
source(here::here("Development/Scripts/df_to_graph_list.R"))

nhtsa_graphs <- df_to_graph_list(papers$text)
```

Let's explore the object.

```{r}
# igraph object level
nhtsa_graphs[[1]][[1]] %>% is.igraph()

# Plot a graph
nhtsa_graphs[[1]][[1]] %>% plot() #haha whoa

# Get Text level
#nhtsa_graphs[[1]][[2]][1]
```

Okay, the object looks like what we want now. Lets compute a graph kernel.

```{r}
source(here::here("Development/Scripts/compute_graph_similarity.R"))
nhtsa_kernel <- matrix(rep(0,48*48), nrow = 48)



for(i in 1:length(nhtsa_graphs)){
  nhtsa_kernel[i,] <- compute_graph_similarity(nhtsa_graphs[[i]])
}
```

Awesome. Im going to try clustering with this real quick.

```{r}
dendro1 <- dist(nhtsa_kernel, method = "manhattan") %>% 
  hclust(method = "complete")

dendro1 %>%
  plot()

papers$k3 <- dendro1 %>% 
  cutree(k = 3)

papers$k5 <- dendro1 %>% 
  cutree(k = 5)

papers$k7 <- dendro1 %>% 
  cutree(k = 7)

papers %>% 
  select(id,k3,k5,k7)
```

```{r}
set.seed(23)
nhtsa_pts <- dist(nhtsa_kernel, method = "manhattan") %>% 
  MASS::isoMDS()

nhtsa_pts$points %>%
  as.data.frame() %>% 
  ggplot(aes(x = V1, y = V2))+
  geom_point()
```


```{r}
nhtsa_graphs[[23]][[2]][1]
nhtsa_graphs[[41]][[2]]


```